Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-10 main.tex
graphs

A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
has an element $\ell(v)\in L$ associated with it, its \bfit{label}.  A
graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
equivalence relation $\samcol$ on $\vG$; each equivalence class is a
\bfit{colour}.  A \bfit{vertex renaming} of $\gG=\tuple{\vG,\eG}$
along a bijection $(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
colouring and/or labelling inherited (i.e., $\hat v\samcol\hat w$ if
$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
theory, we identify graphs modulo vertex renaming.

>>>>

A graph $\gG$ is \bfit{labelled} in a set $L$ if each vertex $v\in\vG$
has an element $\ell(v)\in L$ associated with it, its \bfit{label}.  A
graph $\gG$ is (partially) \bfit{coloured} if it carries a partial
equivalence relation $\samecol$ on $\vG$; each equivalence class is a
\bfit{colour}.  A \bfit{vertex renaming} of $\gG=\tuple{\vG,\eG}$
along a bijection $(\hat\cdot)\colon\vG\to\hat\vG$ is the graph
$\hat\gG=\tuple{\hat\vG,\set{\hat v\hat w\mid vw\in\eG}}$, with
colouring and/or labelling inherited (i.e., $\hat v\samecol\hat w$ if
$v\samecol w$, and $\ell(\hat v)=\ell(v)$). Following standard graph
theory, we identify graphs modulo vertex renaming.
